---
title: "samplingsimulatorr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{samplingsimulatorr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


When learning statistical inference, it is important to    
     
- define important statistical sampling concepts like population distribution, sample distribution, and sampling distribution      
- explain the similarities and differences between the population distribution, sample distribution and sampling distribution.     
- understand how sample sizes may affect the distribution.    
           
The `samplingsimulatorr` package aims to make these steps easy by taking care of the coding part, and so you can focus more on the learning part.  The `samplingsimulatorr` package provides the following functions that will:       
    
- generate a virtual population;       
- draw samples of different sizes;    
- plot the histograms of the sample distribution for each sample size;    
- plot the histograms of the sampling distribution of the mean. 

This document introduces to you the basic tools of `samplingsimulatorr` package and shows you how to use those tools. 

## Use Case Examples

### `generate_virtual_pop`
To start learning sample distribution and sampling distributio, we need first to generate a virtual population. The `generate_virtual_pop` helps you generate a group of virtual population with the distribution of your choice. You just need to fill the size of the population you want to generate, the variable name of that population, and the distribution the population comes from. The function would then produce a nice tibble of the virtual population you sepcified. 

```{r}
library(samplingsimulatorr)

# generate population
pop <- generate_virtual_pop(1000, "height", rnorm, 0, 1)
head(pop)
```
   

### `draw_samples`    
After we have the virtual population, the next thing we need to do is to draw samples from that population. `draw_samples` function helps you draw samples of different sizes from that population. You can also repeatedly draw the samples of the same sizes multiple times to create a sampling distribution. 

```{r}
# the number of replication for each sample size 
reps <- 100
# the sample sizes for each one of the samples
n_s <- c(10, 50, 100)
# create samples
samples <- draw_samples(pop, reps, n_s)
head(samples)
```

### `plot_sample_hist`
After having the samples, we can then plot the sample histograms for different sample sizes using `plot_sample_hist` function.

```{r fig.height=3.5, fig.width=7}
# plot sample histogram
plot_sample_hist(pop, samples, height, n_s)
```

### `plot_sampling_hist`
Since we have drawn the samples of the same size multiple times, we can then plot a nice sampling histogram. The `plot_sampling_hist` creates a grid of sampling distribution histogram of the mean of different sample sizes. 

```{r fig.height=3.5, fig.width=7}
plot_sampling_hist(samples, height, n_s)
```
